Exploring the Presidents Corpus

### 2019-11-07 Source/Paper 1 - Presidents Corpus Paper/PresidentsCorpus.tex
added Abstract

\keywords{Mild Cognitive Impairment \and Alzheimer's Disease \and Machine Learning \and Diagnosis \and Natural Language Processing} 
\bigskip
\begin{abstract}
This paper looks at evidence of cognitive decline in three presidents speeches. Ronald Reagan, who would later go on to receive a diagnosis of Alzheimer's Disease and both George Herbert Walker Bush and Donald Trump who have no known diagnosis of dementia. This study used the methodology used by Berisha and Liss as a starting off point and offers some refinements in how the data was pre-processed, how the features were generated and how the analysis was conducted. We hypothesized that there would be features identified which would decline over time for RR, but not for our controls. We also hypothesised that a non-linear model would map decline more accurately than linear models. We collected data from the Question and Answer portions of the presidents press conferences and used Natural Language Processing to generate features for analysis. We found that there were a number of lexical features that significantly changed over time for RR but did not change for either GHWB or DJT. These features have a foundation in psychological literature and have been linked to cognitive decline in Alzheimer's Disease. Also, we found that non-linear models were able to more accurately map declines in RR's language over time. 
\end{abstract}

@@

Berisha and Liss have developed some very interesting ideas about how we might track changes over time in various lexical features which have been associated with the development of Alzheimer's Disease. We refine these ideas with the aim of exploring the potential for a protocol that can be used for analyzing language deterioration. This study extends the work of Berisha and Liss in a number of ways. Our hypotheses are:
\begin{enumerate}
	\item Language use of RR will be significantly different to our controls (GHWB, DJT).
	\item Modelling the dynamics of lexical features over time can be improved using non-linear models compared to linear models.
\end{enumerate}

@@

\subsubsection{Longitudinal Analysis}
As with Berisha and Liss, we analysed the transcripts over time in order to determine if there was an underlying temporal trend that may indicate that different parts of language increase or decrease over time. In AD, cognitive abilities are said to deteriorate over time and therefore it may be useful to analyse temporal trends that indicate a potential deterioration of cognition. In order to get a accurate measure of deterioration over time, we time stamped each transcript in relation to number of days from the first transcript to the date of the transcript being analysed as the press conferences were not evenly spaced out during the presidencies.

>>>>

\keywords{Mild Cognitive Impairment \and Alzheimer's Disease \and Machine Learning \and Diagnosis \and Natural Language Processing} 
\bigskip
\begin{abstract}
Several research efforts aimed at improving the early diagnosis of Alzheimer's Disease have focused on the longitudinal analysis of lexical features which have been implicated in the pre-clinical development of Alzheimer's Disease. We build on previous studies on this and continue to refine a method of extracting and analyzing language from transcripts with the long-term goal of developing this method for use in clinical practice. We evaluate this method on the unscripted question and answer portions of news conferences from three Presidents. Ronald Reagan, who would later go on to receive a diagnosis of Alzheimer's Disease and both George Herbert Walker Bush and Donald Trump who have no known diagnosis of dementia.  We found that there were several lexical features that significantly changed over time for President Reagan but did not change for either President Bush or President Trump. These features include unique words and noun usage which significantly decrease over time and pronouns (particularly personal pronouns), conjunctions and words which are related to social processes significantly increase over time. No significant trends were found in the analysis of the transcripts of President Bush or President Trump. These features have support in psychological literature and have been linked to cognitive decline in Alzheimer's Disease. We also found that non-linear models were able to more accurately map declines in RR's language over time in comparison to linear models. This work points the way to developing a comparatively non-invasive protocol that can be used in clinical settings that may be able to spot atypical declines in language use over time that may indicate the presence of Alzheimer's Disease.

\end{abstract}

@@

Berisha and Liss have developed some very interesting ideas about how we might track changes over time in various lexical features which have been associated with the development of Alzheimer's Disease. However we feel that cognitive decline in pre-clinical AD is not accurately modeled as a linear process and therefore we explored the application of generalised additive models (GAMs) to this data which have no assumed understanding of the distribution of the data. We refine these ideas with the aim of exploring the potential for a protocol that can be used for analyzing language deterioration.

This study extends the work of Berisha and Liss in a number of ways. Our hypotheses are:
\begin{enumerate}
	\item Language use of RR will be significantly different to our controls (GHWB, DJT).
	\item Modelling the dynamics of lexical features over time can be improved using non-linear models compared to linear models.
\end{enumerate}

@@

\subsubsection{Longitudinal Analysis}
As with Berisha and Liss, we analysed the transcripts over time in order to determine if there was an underlying temporal trend that may indicate that different parts of language increase or decrease over time. In AD, cognitive abilities are said to deteriorate over time and therefore it may be useful to analyse temporal trends that indicate a potential deterioration of cognition. In order to get a accurate measure of deterioration over time, we time stamped each transcript in relation to number of days from the first transcript to the date of the transcript being analysed as the press conferences were not evenly spaced out during the presidencies.
\par
We looked at 
\par 
In order to compare the fit of linear models with
